---
title: "Ahab telemetry data prep"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library ("dplyr")
library("ggplot2")
library(Hmisc)
```


```{r explore}
#explore duration
describe(export_17_$subsession_hours_sum)
  #extreme outliers for subsession_hours_sum should not be possible because this is pinged every 25 hours
lnsubsession_hours_sum <- log(export_17_$subsession_hours_sum)
qplot(lnsubsession_hours_sum, geom="histogram", binwidth=.5)
lnactive_hours_sum<-log(active_hours_sum)
qplot(lnactive_hours_sum, geom="histogram", binwidth=.5)
describe(active_hours_sum)
#active_hours and subsession_hours_sum are moderately related as expected

#explore revenue
describe(search_count_all)
qplot(search_count_all, geom="histogram", binwidth=10)
lnsearch_count_all <- log(search_count_all)
qplot(lnsearch_count_all, geom="histogram", binwidth=1)

#explore intensity
describe(scalar_parent_browser_engagement_total_uri_count_sum)
lnuri_count_sum <- log(scalar_parent_browser_engagement_total_uri_count_sum)
qplot(lnuri_count_sum, geom="histogram", binwidth=.5)

```

```{r nonresponse analysis}
nonresponders <- select(filter(export_17_,hb_engaged == FALSE),c(client_id:num_joined_client_pings))
#show responders vs nonresponders frequency distributions- how bad is our non-response? need k-s tests
ggplot(export_17_, aes(x=lnsubsession_hours_sum, fill=hb_engaged)) +
       geom_histogram(binwidth=.5, alpha=.5, position="identity") +
       labs(title="Frequency Distribution of Subsession Hours",
                                    x ="Natural Log of 2 week's worth of daily subsession hours",
                                    y = "Frequency") +
      guides(fill=guide_legend(title=NULL)) +
      scale_fill_manual(values = c("FALSE" = "orange",
                                 "TRUE" = "blue"),
                             name="hb.engaged.rename",
                         breaks=c("FALSE", "TRUE"),
                         labels=c("Non-responders", "Clicked through to survey")
                  )
ggplot(export_17_, aes(x=lnsearch_count_all, fill=hb_engaged)) +
       geom_histogram(binwidth=.5, alpha=.5, position="identity") +
       labs(title="Frequency Distribution of Search Counts",
                                    x ="Natural Log of 2 week's worth of daily number of searches",
                                    y = "Frequency") +
      guides(fill=guide_legend(title=NULL)) +
      scale_fill_manual(values = c("FALSE" = "orange",
                                 "TRUE" = "blue"),
                             name="hb.engaged.rename",
                         breaks=c("FALSE", "TRUE"),
                         labels=c("Non-responders", "Clicked through to survey")
                  )
ggplot(export_17_, aes(x=lnuri_count_sum, fill=hb_engaged)) +
       geom_histogram(binwidth=.5, alpha=.5, position="identity") +
       labs(title="Frequency Distribution of URI Count",
                                    x ="Natural Log of 2 week's worth of daily URI count",
                                    y = "Frequency") +
      guides(fill=guide_legend(title=NULL)) +
      scale_fill_manual(values = c("FALSE" = "orange",
                                 "TRUE" = "blue"),
                             name="hb.engaged.rename",
                         breaks=c("FALSE", "TRUE"),
                         labels=c("Non-responders", "Clicked through to survey")
                  )
  
```

```{are non responders and responders from same distribution?}
#working on this:
ks.test(x, y, ...,
        alternative = c("two.sided", "less", "greater"),
        exact = NULL)
```
        
```{visualizing selection bias related to days survey open}
##replace ln duration0 with var for same survey day ln subsesion hours
ggplot(export_17_, aes(x=hb_submission_date_s3, y=lnduration0, color=hb_engaged)) +
   xlim(20180913,20180926)+
    geom_point(shape=1, position=position_jitter(width=.2)) +
   geom_smooth (method=lm)+
   labs(title="Subsession length of survey invitees over time",
   y ="Natural Log of subsession length on date of survey",
   x = "Date of survey") +
   guides(fill=guide_legend(title=NULL)) +
   scale_color_manual(values = c("FALSE" = "orange", "TRUE" = "blue"),
           name=(""),
            breaks=c("FALSE", "TRUE"),
           labels=c("Non-responders", "Clicked through to survey")
 )

             
        